---
title: "Learning to program with mineR"
author: "David Smith"
date: "May 25, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Learn to program in Minecraft with mineR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The mineR package provides a simple interface to the Minecraft world. Use R functions
to connect with a MineCraft server and control the world within.


The purpose of this package is to teach new programmers about R. See the effect of your programs
directly in the Mindcraft world!

### About Minecraft

To use the mineR package, you will need to set up your own Minecraft server.

Here's how to download and install a server.

Here's how to get the Minecraft client to connect. You must use the PC version, not the "Pocket Minecraft" or Windows 10 version.

## Your first mineR adventure

Here is a quick tutorial demonstrating basic mineR commands.

Connect to the world. For this you will need to know the IP address of your server.

```
mc_connect("52.168.1.2") # use the IP of your server here
```

To check you have successfully connected to the world, you can try chatting:

```r
chatPost("Message goes to all players.")
```

Each player in the world gets a Player ID. If you're the only player in the world,
this is easy. But if there are multiple players, the easiest way to find your ID is 
to sign out of the server and then sign in again. Your player ID will then be the last
one on the list.

```r
myid <- tail(getPlayerIds(),1) 
```

Once you have a Player ID, you can move the player around.

```r
myloc <- getPlayerPost(myid)
setPlayerPos(myloc[1],myloc[2],myloc[3]+100,player_id=myid) # move player 10 tiles in the air
```



## mineR commands

Functions you can use:

* `mc_connect`: Connect to a MineCraft server
* `getPlayerIds`: Get a list of players in the world
* 


## Suggestions for writing your own programs with mineR

Put your picture on a Minecraft wall!

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
