---
title: "Learning to program with mineR"
author: "David Smith"
date: "May 25, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Learn to program in Minecraft with mineR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The mineR package provides a simple interface to the Minecraft world. Use R functions to connet with a MineCraft server and control the world within.


The purpose of this package is to teach new programmers about R. See the effect of your programs
directly in the Mindcraft world!

## About Minecraft

Info on getting Minecraft and setting up a server

# Your first mineR adventure

Quick tutorial demonstrating basic Minecraft commands

# mineR commands

Overview of tools

# Suggestions for writing your own programs with mineR

Put your picture on a Minecraft wall!

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
